Neutron transport methods can be loosely classified into two domains: deterministic and Monte Carlo.
The latter of these has been dubbed the gold standard for simulations because it directly solves the governing \acrlong{bte} directly through the simulation of distinct particles.
Though embarrassingly parallelizable, Monte Carlo methods are notoriously slow to converge and can still yield high uncertainty in areas of low flux.
Deterministic methods, alternatively, discretize the phase space to numerically approximate the solution.
They are more difficult to mathematically formulate but can produce an acceptable solution in a fraction of the time it takes for Monte Carlo methods.

The field of computer-graphics has long been interested in the solution of global transport problems to accurately render scenes in animation and video games.
Since the development and release of consumer-available ray tracing hardware, significant effort has been put towards the development of realtime global illumination solution methods.
One of these methods, called \acrlong{rc}, is a novel approach to solving these problems that also promises impressive scalability on modern graphical processing unit (GPU) hardware.

In this proposal, we present a comprehensive discussion and analysis of the theory of \glspl{rc} to motivate our proposed work.
We then outline our implementation plans (and thought process) and describe how we will demonstrate the effectiveness of \glspl{rc} for global neutron transport using selected benchmark problems.